\documentclass[11pt]{article}

%%%%%%%%%%%%%%% PACKAGES %%%%%%%%%%%%%%%

\usepackage{url}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage{enumerate}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amscd}
\usepackage{amsrefs}
\usepackage[affil-it]{authblk}
\usepackage{mathtools}

%%%%%%%%%%%%%%% TITLE/AUTHOR INFORMATION %%%%%%%%%%%%%%%

\title{Digital Signal Processing}
\author{Marvin Lin}
\date{\today}
\affil{Portland Community College}

%%%%%%%%%%%%%%% CUSTOM FORMAT %%%%%%%%%%%%%%%

\setlength{\textwidth}{6.5in}
\setlength{\textheight}{9in}
\setlength{\evensidemargin}{0in}
\setlength{\oddsidemargin}{0in}
\setlength{\topmargin}{+.4in}

\setlength{\oddsidemargin}{0.in}
\setlength{\evensidemargin}{0.in}
\setlength{\textwidth}{6.46in}
\setlength{\textheight}{8.4in}

\usepackage[margin=2.5cm]{geometry}

%%%%%%%%%%%%%%% PREAMBLE %%%%%%%%%%%%%%%

\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\DeclareMathOperator{\rank}{rank}               % Rank
\DeclareMathOperator{\vol}{vol}                 % Volume
\DeclarePairedDelimiter\abs{\lvert}{\rvert}     % Absolute Value

%%%%%%%%%%%%%%% BEGIN DOCUMENT %%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%% TITLE %%%%%%%%%%%%%%%

\maketitle

%%%%%%%%%%%%%%% ABSTRACT %%%%%%%%%%%%%%%

\begin{abstract}

Digital signal processing (DSP) is integral to many of the computational tools we use in our everyday lives. Ranging from voice assistants, sensor data processing, to even data compression, digital processors are used regularly to perform various signal processing methods. Data is sampled in the time, space, or frequency domain and utilize linear transformations to appropriately filter and adjust the signal to specification. DSP can be seen in voice assistants such as Siri, Alexa, or Google Assistant. Voice, an analog signal, is converted with an analog-to-digital converter after data sampling, which then characterized as various commands (ie. "yes" or "no") utilizing DSP. Similarly, file and data compression software utilizes linear transformations to digitally process data to fit a smaller file size.

\end{abstract}

%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%

\section{TEMPORARY}

For example, I may have written a book. \cite{book:author}. Or I may have viewed a website. \cite{website:topic}.

%%%%%%%%%%%%%%% BIBLIOGRAPHY %%%%%%%%%%%%%%%

\bibliographystyle{plain} % We choose the "plain" reference style
\bibliography{refs} % Entries are in the "refs.bib" file

%%%%%%%%%%%%%%% END DOCUMENT %%%%%%%%%%%%%%%

\end{document} 